Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph\tnoteref{t1,t2}

### 2016-04-29 curvature.tex
added funding to acknowledgements as well

\section{Acknowledgements}
The authors would like to thank Alex Gavruskin, Vladimir Minin, and Bianca Viray for helpful discussions.
They are also grateful to the authors of the SAGE and GAP4 software, especially Alexander Hulpke.
A preliminary version of this work appeared in the 2016 Proceedings of the Thirteenth Workshop on Analytic Algorithmics and Combinatorics (ANALCO).
The authors would like to thank the conference organizers, reviewers, and attendees for helpful comments and discussions that greatly improved this full version of our work.

>>>>

\section{Acknowledgements}
This work was funded by National Science Foundation award 1223057.
Chris Whidden is a Simons Foundation Fellow of the Life Sciences Research Foundation.

The authors would like to thank Alex Gavruskin, Vladimir Minin, and Bianca Viray for helpful discussions.
They are also grateful to the authors of the SAGE and GAP4 software, especially Alexander Hulpke.
A preliminary version of this work appeared in the 2016 Proceedings of the Thirteenth Workshop on Analytic Algorithmics and Combinatorics (ANALCO).
The authors would like to thank the conference organizers, reviewers, and attendees for helpful comments and discussions that greatly improved this full version of our work.
